Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Add bio info for myself.

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/braker_headshot.jpg}}]
  {Roger A. Braker} is so happy that all this is almost done.

>>>>

\begin{IEEEbiography}
  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/braker_headshot.jpg}}]
  {Roger A. Braker} earned the B.A. degree in physics from the University of Oklahoma in 2005 and the M.S. degree in electrical engineering from the University of Colorado in 2017.
  Since 2014, he has been a graduate student in the Electrical, Computer, and Energy Engineering
  Department at the University of Colorado Boulder.
